Maybe Slipstreams $|$-o-$|$

### 2014-03-07 paper.tex
Changes made from librry

\title{Usable Functional Reactive Programming with Slipstreams}
\author[*]{Morgan McDermott}
\author[**]{John Carlyle}
\affil[*]{University of flightless dragons}
\affil[**]{University of angry bees}

@@

\section{Abstract}
We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world. We allow signal networks to be dynamic by modeling them as higher order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe. All signal values are modeled as $Maybe$ values to allow for defined behavior in the face of disrupted signals, and to reference signal values before they have any reasonable value. We also specify a DSL that uses this FRP model, allowing a programmer to easily design signal networks to accomplish tasks by specifying layers and how the layers interact. Our implementation builds on previous work by being more practical. The DSL arises naturally from our definition of FRP, is simple to use and requires only limited knowledge of the underlying FRP concepts.

@@

Secondly, how do we model the changing requirements for interfaces? If the user presses a button to submit a query to the server, the server could respond in a way indicating that they need to update the interface on the page. Perhaps we need to create more buttons that could perform different server queries. In order to solve this, we must define a flexible, dynamic FRP network that can modify itself. Elerea solves this by providing Higher Order Streams.

@@

\section{Our contributions}
\subsection{Maybe Streams}
Merging streams and wormholes and making an implementation of the whole thing practical. Making it based in theory so its not a giant mess like bacon.js. Monad streams woo!

\subsection{Higher-order streams}

@@

\subsection{Higher-order streams}
Work has already been done on higher order streams \cite{HighOrderStreams}. Higher order streams are nessisary for having a dynamic network. Dynamic networks are required

>>>>

\title{Maybe Slipstreams $|$-o-$|$}
\author[*]{Morgan McDermott}
\author[**]{John Carlyle}
\affil[*]{University of flightless dragons}
\affil[**]{University of angry bees}

@@

\section{Abstract}
We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world. We allow signal networks to be dynamic by modeling them as higher-order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe. All signal values are modeled as $Maybe$ values to allow for defined behavior in the face of disrupted signals, and to reference signal values before they have any reasonable value. We also specify a DSL that uses this FRP model, allowing a programmer to easily design signal networks to accomplish tasks by specifying layers and how the layers interact. Our implementation builds on previous work by being more practical. The DSL arises naturally from our definition of FRP, is simple to use and requires only limited knowledge of the underlying FRP concepts.

@@

Secondly, how do we model the changing requirements for interfaces? If the user presses a button to submit a query to the server, the server could respond in a way indicating that they need to update the interface on the page. Perhaps we need to create more buttons that could perform different server queries. In order to solve this, we must define a flexible, dynamic FRP network that can modify itself. Elerea solves this by providing Higher-Order Streams.

@@

\section{Our contributions}
Our contributions are basically jsut reworking the bind in a stream monad to map between layer sets. Also each value is wrapped in a maybe, revolutionary. This allows safe access to resources that have not yet been created in a dynamic network setting. It also allows for safe handling of volatile resources such as HTTP requests or accessing other error prone procedures. Convenience elements have been added such as the aggregator, which allows for dynamic seeming networks without any modification to the underlying structure. This is possible due to the addition of the maybe value to every stream.
\subsection{DSL Grammar}
\footnotesize
\begin{align*}
  Statement ::=& ~V \leftarrow Expression &\text{Variable assignment}\\
  |& ~Expression &\text{Single expression}\\
  Expression ::=& ~SignalNet &\text{A signal network}\\
  |& SimpleExpr &\text{An expression}\\
  SignalNet ::=& ~( Exprs ) \rightarrow SignalNet &\text{Compose layers}\\
   |& ~(Exprs ) &\text{Single layer} \\
  Exprs ::=& ~SimpleExpr ~,~ Exprs &\text{List of expressions}\\
  |& ~SimpleExpr &\text{Single expression}\\
  SimpleExpr ::=& ~L[``Javascript code''] &\text{Lift}\\
  |& ~ @V &\text{Get}\\
  |& ~ *V(SimpleExpr) &\text{Put}\\ 
  |& ~ V( Exprs ) &\text{Function call}\\
  V ::=& ~Word~Characters &\text{Variable}
\end{align*}
\normalsize
As you can see our grammar is exteremly simple and contributes basically 1 monad with bind. Thats it. PhD Please.

\subsection{Maybe Streams}
Merging streams and wormholes and making an implementation of the whole thing practical. Making it based in theory so its not a giant mess like bacon.js. Monad streams woo!

\subsection{Higher-order streams}
Streams composed with streams oh my. Gotta look out for those undefined values. The value of composed streams is the diagonal of the matrix formed by the stream values. Boop:

\begin{align*}
  \langle &\langle \mathbf{v_{00}} ~ v_{01} ~ v_{02} ~ v_{03} ~ ... ~ \rangle \\
  &\langle \perp ~ \mathbf{v_{11}} ~ v_{12} ~ v_{13} ~... ~ \rangle \\
  &\langle \perp ~ \perp ~ \mathbf{v_{22}} ~ v_{23} ~ ...  ~ \rangle \rangle
\end{align*}

Better idea to avoid wasted space and complex ge

\begin{align*}
  \langle &\langle \mathbf{v_{00}} ~ v_{01} ~ v_{02} ~ v_{03} ~ ... ~ \rangle \\
  &\langle  \mathbf{v_{11}} ~ v_{12} ~ v_{13} ~ v_{14} ~ ... ~ \rangle \\
  &\langle  \mathbf{v_{22}} ~ v_{23} ~ v_{24} ~ v_{25} ~ ...  ~ \rangle \rangle
\end{align*}

@@

\subsection{Higher-order streams}
Work has already been done on higher-order streams \cite{HighOrderStreams}. Higher-order streams are nessisary for having a dynamic network. Dynamic networks are required
